---
title: "Assignment1"
output: html_document
---


```{r message=FALSE}
##Loading Libraries
library(GenomicRanges)
library(rtracklayer)
library(RColorBrewer)
```

```{r}
#Read bed files
k27ac <- import.bedGraph(con="K27Ac_D7_Th1-W200-G200-E200-island.bedgraph", asRangedData=FALSE)
dat3 <- import.bed(con="3merge.bed", asRangedData=FALSE)
overlap <- import.bed(con="5merge.bed", asRangedData=FALSE)
k4m3 <- import.bedGraph(con="K4m3_Th1_72h-W200-G200-E200-island.bedgraph", asRangedData=FALSE)
dat4 <- import.bed(con="4merge.bed", asRangedData=FALSE)
overlap2 <- import.bed(con="6merge.bed", asRangedData=FALSE)
```

```{r}
#Calculate Percentages
total <- sum(width(k27ac))
part <- sum(width(dat3))
part3 <- sum(width(overlap))

total2 <- sum(width(k4m3))
part2 <- sum(width(dat4))

part4 <- sum(width(overlap2))

(ans3 <- part/total)
(ans4 <- part2/total2)
(ans5 <- part3/total2)
(ans6 <- part4/total)
```

```{r echo=FALSE}
##Loading Libraries
#Function to put graphs in 2x2 Grid
mypar2 <- function(a=1,b=1,brewer.n=8,brewer.name="Dark2",cex.lab=1,cex.main=1.2,cex.axis=1,mar=c(2.5,2.5,1.6,1.1),mgp=c(1.5,.5,0),...){
  require(RColorBrewer)
  par(mar=mar,mgp=mgp,cex.lab=cex.lab,cex.main=cex.main,cex.axis=cex.axis)
  par(mfrow=c(a,b),...)
  palette(brewer.pal(brewer.n,brewer.name))
}
```

```{r}
##Creating Graphs
mypar2(2,2)
slices <- c(part, total) ##Pie chart 1
lbls <- c("TSS", "Total")
pie(slices, labels = lbls, main="A H3K4me3 Marks within 5kbp of TSS")
slices <- c(part2, total2) ##Pie chart 2
lbls <- c("TSS", "Total")
pie(slices, labels = lbls, main="B H3K27ac Marks within 5kbp of TSS")
slices <- c(part2, total2) ##Pie chart 3
lbls <- c("Overlap", "Total")
pie(slices, labels = lbls, main="C H3K4me3 Overlapping H3K27ac")
slices <- c(part3, total) ##Pie chart 4
lbls <- c("Overlap", "Total")
pie(slices, labels = lbls, main="D H3K27ac Overlapping H3K4me3")
```

Figure 1. A shows the percentage of H3K4Me3 marks within 5 kbp on either side of the transcription start sites of every gene over the entire H3K4Me3 coverage of the genome. B shows the percentage of H3K27ac marks within 5 kbp on either side of the transcription start sites of every gene over the entire H3K27ac coverage of the genome. C shows the percentage of H3K4me3 coverage that overlaps the coverage of H3K27ac and D shows the percentage of H3K27ac coverage over the entire coverage of H3K4me3.

